Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-09-15 article/sections/application_353ghz.tex
updated the introductory discussion in the numerical implementation section

\subsection{Application of Planck 353 Ghz polarization maps}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-real-space-disc8apo3.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-real-space-disc8apo3.pdf}}
\caption{}
\label{fig:353ghz-eb-maps}
\end{figure}
%

>>>>

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Application to Planck 353 Ghz polarization maps}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-real-space-disc8apo3.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-real-space-disc8apo3.pdf}}
\caption{}
\label{fig:353ghz-eb-maps}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Scaling and future prospects}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$. The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
\label{fig:disc_rad_healpix_numpix}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------

### 2017-09-15 article/sections/kernel_discussion.tex
updated the introductory discussion in the numerical implementation section

\section{Visualizing the real space operators} \label{sec:visualize_operator}
We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $. Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels. These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$. The resultant functions are depicted in \fig{fig:beta_kernel}. Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$). 
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}. These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$. The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
\label{fig:beta_kernel}
\end{figure}
%
We recall that the fields E \& B are scalar and hence immune to coordinate definitions. The locally defined Stokes parameters however necessarily depend on the coordinate definition. Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars. The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B. Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.

@@

\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels. To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$. The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}. All the function have been normalized such that their global maxima is set to unity. Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel. 
%
\begin{figure}[!t]
\centering
\subfigure[]{\includegraphics[width=1.0\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$. The curves for each of these functions have been normalized such that the maximum of the curve is set to unity. The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum. The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions. While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%
We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$. We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.

>>>>

\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $. Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels. These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$. The resultant functions are depicted in \fig{fig:beta_kernel}. Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$). 
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}. These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$. The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
\label{fig:beta_kernel}
\end{figure}
%
We recall that the fields E \& B are scalar and hence immune to coordinate definitions. The locally defined Stokes parameters however necessarily depend on the coordinate definition. Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars. The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B. Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.

@@

\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels. To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$. The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}. All the function have been normalized such that their global maxima is set to unity. Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel. 
%
\begin{figure}[!t]
\centering
\subfigure[]{\includegraphics[width=1.0\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$. The curves for each of these functions have been normalized such that the maximum of the curve is set to unity. The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum. The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions. While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%
We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$. We find that the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.

### 2017-09-15 article/sections/numerical_implementation.tex
updated the introductory discussion in the numerical implementation section

In this section we study the effects of localizing the convolution kernels on the inferred E and B mode maps and their power spectra. We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters. To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$. Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels. $f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}. ${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$, given in \app{sec:asymptotic_f}. As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}. We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}. Given these  inputs we evaluate the convolutions as simple Reimann sums. We repeat this procedure for each pixel on the Healpix map.

\revisit{We use the CMB spectra for the fiducial cosmology. Specifically we restrict our analysis on lensing generated B-mode spectra.}  For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise. To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.  Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$. We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs. We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise. Note that the Healpix evaluations are equivalent to carrying out the convolution over the full sphere (i.e. $\beta_o=\pi$).  We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}

%
\begin{figure}[!h] 
\centering
\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/emap-healpix.pdf}}
\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/emap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/emap-diff.pdf}}
\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-healpix.pdf}}
\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-diff.pdf}}
\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix. {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$. {\textit Right:} Difference between the maps shown in the left and middle columns. Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
\label{fig:eb-maps-compare}
\end{figure}
%
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:eq-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Extracting Equ and Bqu maps}
%
\begin{figure}[!h] 
\centering
\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}

@@

%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/equ-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:equ-bqu-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Scaling and future prospects}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$. The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
\label{fig:disc_rad_healpix_numpix}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------

>>>>

In this section we study the effects of localizing the convolution kernels on the inferred E and B mode maps and their power spectra. We have developed a Python script to compute these local convolution over Stokes Q \& U parameters. To carry out this numerical exercise, we pre-compute the radial part of the kernels, namely the function: $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta)$. We use the python routine {\textit scipy.special.lpmn} for the numerical evaluation of the associated Legendre polynomial functions required to compute the respective radial kernels following equations \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker}. Specifically while computing the functions ${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta)$ in the vicinity of $\beta=0~\&~\pi$, we use the limiting forms of the respective functions given in \app{sec:asymptotic_f}. As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}. We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are used to calculate the corresponding Euler angles using \eq{eq:fn_euler}. Given these inputs we evaluate the convolutions as simple Reimann sums. We repeat this procedure for each pixel on the Healpix map to yielding the resultant maps (E ,B, Q, U).

\revisit{We use the CMB spectra for a fiducial cosmology and restrict our analysis on lensing induced B-mode spectra.}  For the results presented in the following sections we carry out our analysis on CMB maps at Healpix resolution of ${\rm NSIDE}=64$. In order to understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.  Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=22.5^{\circ}$. \revisit{We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs. }We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise. Note that the Healpix evaluations are equivalent to carrying out the convolutions over the full sphere (i.e. $\beta_o=\pi$).  We compare these maps to the reference maps and their respective spectra, to quantitatively understand the effect of the imposed radial cutoff on the convolutions.

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Constructing E \& B maps using local convolutions}

%
\begin{figure}[!h] 
\centering
\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/emap-healpix.pdf}}
\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/emap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/emap-diff.pdf}}
\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-healpix.pdf}}
\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-diff.pdf}}
\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix. {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$. {\textit Right:} Difference between the maps shown in the left and middle columns. Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
\label{fig:eb-maps-compare}
\end{figure}
%
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:eq-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Separating Stokes Q \& U maps corresponding to E \& B modes of polarization}
%
\begin{figure}[!h] 
\centering
\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}

@@

%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/equ-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:equ-bqu-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Multipole filtering using spatial convolutions}
%--------------------------------------------------------
%--------------------------------------------------------
